### 2014-05-21 intro.tex
Hari fixes

After investigating many candidate signals, we have ended up with
computer-generated algorithms that collect four congestion signals
(Section~\ref{ss:signals}). \textbf{None of these signals} is
collected by traditional TCP congestion-control schemes. Our
simulation experiments indicate each signal is individually valuable on
top of the other three.

@@

Traditional congestion-control algorithms are window-based and
ack-clocked.~\cite{Srikant} Some proposed algorithms use
\emph{pacing}---transmitting packets according to an internal clock at
the sender---but the performance of these algorithms can display
counter-intuitive weaknesses.~\cite{understandingpacing}

@@

Netflix, said to account for the majority of Internet traffic in the
United States, is working on improving its congestion control in the
context of rate selection for progressive-download video, after
research findings that its existing algorithm could produce poor results.~\cite{huang2012confused}

>>>>

After investigating many candidate signals, we have ended up with
computer-generated algorithms that collect four congestion signals
(Section~\ref{ss:signals}):

\begin{enumerate}

\item An exponentially-weighted moving average (EWMA) of the
  interarrival time between new acknowledgments received ({\tt
    ack\_ewma}), where each new sample contributes 1/8 of the weight
  of the moving average.

\item In some RemyCCs, where the goal is operation over a broad range
  of networks, we consider the same feature but with a longer-term
  moving average, using a weight of 1/256 for the newest sample ({\tt
    slow\_ack\_ewma}).

\item An exponentially-weighted moving average of the time between TCP
  sender timestamps reflected in those acknowledgments ({\tt
    send\_ewma}), again with a weight of 1/8 to each new sample.

\item The ratio between the most recent RTT and the minimum RTT seen
  during the current connection (\tt{rtt\_ratio}).

\end{enumerate}

\textbf{None of these signals} is collected by traditional TCP
congestion-control schemes. Our simulation experiments indicate each
signal is individually valuable on top of the other three.

@@

Traditional congestion-control algorithms are window-based and
ack-clocked~\cite{Srikant}. Some proposed algorithms use
\emph{pacing}---transmitting packets according to an internal clock at
the sender---but the performance of these algorithms can display
counter-intuitive weaknesses~\cite{understandingpacing}.

@@

Netflix, said to account for the majority of Internet traffic in the
United States, is working on improving its congestion control in the
context of rate selection for progressive-download video, after
research findings that its existing algorithm could produce poor results~\cite{huang2012confused}.
